Automated Formal Synthesis of Provably Safe Digital Controllers for Continuous Plants

### 2019-07-09 automatica/paper.tex
response

\begin{theorem}
  \label{th:safety}
\rev{Assuming that the initial state is in the safe set, }
if a controller is safe for each of the corner cases of the hypercube of allowed initial states, 
i.e., the vertex states, then it is safe for any initial state in the hypercube. 
\end{theorem}
\begin{proof}
Consider the set of initial states, $X_0$, which we note is convex since it is a hypercube. 
Name $v_i$ its vertices, where $i=1,\ldots, 2^n$.  
Thus any point $x \in X_0$ can be expressed by convexity as $x = \sum_{i=1}^{2^n} \alpha_i v_i$, 
where $\sum_{i=1}^{2^n} \alpha_i =1$. Then if $x_0=x$, we obtain 
\begin{align*}
x_k   &= (A_d - B_d K)^k x = (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i \\
      &= \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i = \sum_{i=1}^{2^n} \alpha_i x_k^i, 
 \end{align*}     
%
where $x_k^i$ denotes the trajectories obtained from the single vertex
$v_i$.  We~conclude that any $k$-step trajectory is encompassed, within a
convex set, by those generated from the vertices. 
\rev{Recall that we have assumed that the initial set lies within the safe set, and that both are (convex) hyper-boxes. The conclusion follows. }
\qed
\end{proof}
Summarising, we only need to check $2^n$ initial states, 
where $n$ is the dimension of the state space (number of continuous variables).

@@

\begin{proof}
%
An asymptotically stable model is known to have converging dynamics.  Assume the
closed-loop matrix eigenvalues are not repeated (which is sensible to do,
since we select them).  The distance of the trajectory from the reference
point (which, for linear models, is the origin) decreases over time within subspaces related to real-valued
eigenvalues; however, this is not the case in general when dealing with
complex eigenvalues.  Consider the closed-loop matrix that updates the
states in every discrete time step, and select the eigenvalue $\vartheta$
with the smallest (non-trivial) imaginary value.  Between every pair of
consecutive time steps $k\,T_s$ and $(k+1)\,T_s$, the dynamics projected on
the corresponding eigenspace rotate $\vartheta T_s$ radians.  Thus, taking
$\overline{k}$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, after
$k{\geq}\overline{k}$ steps we have completed a full rotation, which results
in a point closer to the origin.  The synthesized $\overline{k}$ is the completeness threshold. 
\rev{[I will try to spin this more formally. ]}
\qed 
%
\end{proof}

>>>>

\begin{theorem}
  \label{th:safety}
\rev{Assuming that the initial set is included within the safe set, }
if a controller is safe for each of the corner cases of the hypercube of allowed initial states, 
i.e., the vertex states, then it is safe for any initial state in the hypercube. 
\end{theorem}
\begin{proof}
Consider the set of initial states, $X_0$, which we note is convex since it is a hypercube. 
Name $v_i$ its vertices, where $i=1,\ldots, 2^n$.  
Thus any point $x \in X_0$ can be expressed by convexity as $x = \sum_{i=1}^{2^n} \alpha_i v_i$, 
where $\sum_{i=1}^{2^n} \alpha_i =1$. Then if $x_0=x$, we obtain 
\begin{align*}
x_k   &= (A_d - B_d K)^k x = (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i \\
      &= \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i = \sum_{i=1}^{2^n} \alpha_i x_k^i, 
 \end{align*}     
%
where $x_k^i$ denotes the trajectories obtained from the single vertex
$v_i$.  We~conclude that any $k$-step trajectory is encompassed, within a
convex set, by those generated from the vertices. 
\rev{Recall that we have assumed that the initial set lies within the safe set, and that both are (convex) hyper-boxes. The conclusion follows. }
\qed
\end{proof}
Summarising, we only need to check $2^n$ initial states, 
where $n$ is the dimension of the state space (number of continuous variables).

@@

\begin{proof}
%
An asymptotically stable model is known to have converging dynamics.  
Assume that the eigenvalues of the closed-loop matrix are not repeated: this is sensible assumption to raise, 
since the eigenvalues are selected by the user. \rev{ The distance of the trajectory from the reference
point (which, for linear models, is the origin) decreases over time within subspaces related to real-valued
eigenvalues (say, $\theta < 0$): this can be shown considering the exponential $e^{\theta t} x_0$ ($x_0$ being the initial condition), 
which envelops the model dynamics within subspaces and is monotonically decreasing. } 
\rev{ However, this monotonic decrease cannot be ensured in general when dealing with complex eigenvalues. } 
Consider the closed-loop matrix that updates the
states in every discrete time step, and select the eigenvalue $\vartheta$ 
with the smallest (non-zero) imaginary part.  
Between any pair of consecutive time steps $k\,T_s$ and $(k+1)\,T_s$, the dynamics projected on
the corresponding eigenspace rotate of $\vartheta T_s$ radians.  Thus, taking
$\overline{k}$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, after
$k{\geq}\overline{k}$ steps the model trajectory has completed a full rotation \rev{within the relevant eigenspace}: 
this results in a point closer to the origin, \rev{as shown in Fig. \ref{fig:ct}}.  The synthesized $\overline{k}$ is thus a completeness threshold: 
\rev{indeed, since we have selected $\vartheta$ to be the complex eigenvalue with smallest imaginary part, 
any other pair of complex eigenvalues will correspond to dynamics that rotate faster within the corresponding eigenspace. 
Hence, $\overline{k}$ will again represent a completeness threshold. }
\qed 
%
\end{proof}
